% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\usepackage[backend=bibtex]{biblatex}
\usepackage[usenames,dvipsnames]{xcolor}
\addbibresource{pubs.bib}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------



\begin{document}



\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://researcher.ibm.com/researcher/view.php?person=us-jjortiz}{\LARGE Jorge Ortiz, Ph.D.}} & \href{mailto:jortiz@alum.mit.edu}{jortiz@alum.mit.edu}\\
	{\footnotesize \texttt{\colorbox{gray}{[601 West 57 Street, Apt 5Q, NY, NY 10019]}}} & \href{http://researcher.ibm.com/researcher/view.php?person=us-jjortiz}{http://jorgeortizphd.info} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
        \item
            \ressubheading{\href{}{University of California, Berkeley}}{Berkeley, CA}{\href{}{Doctor of Philosophy in Computer Science}; \href{}}{May. 2010 -- Dec. 2013}
                { \footnotesize
				\begin{itemize}
					\resitem{Dissertation: A Platform Architecture for Sensor Data Processing and Verification in Buildings}
				\end{itemize}
				}
        \item
            \ressubheading{\href{}{University of California, Berkeley}}{Berkeley, CA}{\href{}{Masters of Science in Computer Science}; \href{}}{Aug. 2007 -- May 2010}
                { \footnotesize
				\begin{itemize}
					\resitem{Thesis: Multichannel Reliability Assessment in Real World WSNs}
                    \resitem{Relevant Courses: Advanced Systems Seminar I \& II, Graduate Networking, Sensor Networks Seminar, Combinatorial Algorithms, Parallel Computation Algorithms, Statistical Learning Theory, Practical Machine Learning.}
				\end{itemize}
				}
       \item
            \ressubheading{\href{}{Massachusetts Institute of Technology}}{Cambridge, MA}{\href{}{Bachelors of Science in Computer Science and Engineering}; \href{}}{Aug. 1999 -- May 2003}
                { \footnotesize
				\begin{itemize}
					\resitem{Thesis: Connection Oriented Routing Environment (CORE): A Generalized Device         Interconnect}
				\end{itemize}
				}
    \end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{itemize}

        \item 
			\ressubheading{\href{http://www.research.ibm.com/}{IBM Research}}{Yorktown Heights, NY}
				{Research Staff Member}{Dec. 2013 -- Present}
				{ \footnotesize
				\begin{itemize}
                    \resitem{Research work on a variety of topics related to distributed systems, mobile sensing, cloud-based middleware architectures, and machine learning. }
				\end{itemize}
				}


        \item 
			\ressubheading{\href{https://spire.com/}{Spire}}{San Francisco, CA}
				{Senior Software Engineer}{Jan. 2013 -- Sept. 2013}
				{ \footnotesize
				\begin{itemize}
                    \resitem{Designed and wrote communication kernel for arduino-based, nano satellites.}
				\end{itemize}
				}

		\item 
			\ressubheading{\href{http://www.oracle.com}{Oracle Corporation}}{Burlington, MA}
				{Software Engineer}{Sept. 2003 -- Feb. 2007}
				{ \footnotesize
				\begin{itemize}
                    \resitem{Assisted in designing, debugging, and maintaining several features in Oracle Enterprise Planning and Budgeting (EPB) software suite; include, but not limited to the setup of PL/SQL packages, schemas, and interfaces to the Java\-based UI.}
				\end{itemize}
				}

				
		
\end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{\href{http://www.derekhildreth.com/portfolio.php}{Skills}}
	\begin{description}
		\item[Proficient in:]{Java, Python, C
		}
		\item[Experience/Familiar with:]{ \footnotesize
            C++, Javascript, Perl, NesC, TinyOS,
            IEEE 802.11, 802.15.4, Android development
		}
        \item[Fluent in:] { \footnotesize
            Spanish
		}
	\end{description} % End Skills list

\resheading{Internships}
	\begin{itemize}

        \item 
			\ressubheading{\href{}{Charles River Analytics}}{Cambridge, MA}
				{Research Intern}{Jun. 2003 -- Sept. 2003}
				{ \footnotesize
				\begin{itemize}
                    \resitem{Designed genetic algorithms for optimizing flight paths under various weather conditions.  Tested algorithms in a cluster.  Wrote cluster management components of simulator.}
				\end{itemize}
				}


        \item 
			\ressubheading{\href{}{IBM Research}}{Cambridge, MA}
				{Research Intern}{May 2002 -- Aug. 2002}
				{ \footnotesize
				\begin{itemize}
                    \resitem{Designed backend of prototype mobile email client.  Designed usability experiments and collected data about fundamental components in the design.}
				\end{itemize}
				}

        \item 
			\ressubheading{\href{}{Merrill Lynch}}{New York, NY}
				{Summer Analyst}{May -- Aug. 2000/2001}
				{ \footnotesize
				\begin{itemize}
                    \resitem{Design and wrote internal websites for Technology Infrastructure Services- Network Services Group (TIS-NS) the Corporate and Institutional Client Group Desktop Engineering (CDE).}
				\end{itemize}
				}

	\end{itemize}  % End Experience list



%%%%%%%%%%%%%%%%%%%%%%

\resheading{Select Publications}
\nocite{*}                                          % Print all publications.
\printbibliography[heading=none]



\end{document}



